---
title: "BIS15L_AI_class"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
Today, we're exploring how AI can aid in writing, comprehending and troubleshooting our R code. AI is a very valuable tool, but it's important not to rely on it entirely. Building a strong R foundation is still important. These AI tools are not perfect and can be inaccurate solutions. In addition these tools can't read our minds, so understanding R helps us generate better prompts to get better responses. In short, AI should be used as a tool, not a crutch. Additionally, do not forget about other useful resources like Stack Overflow/Exchange, online tutorials, and GitHub issues pages for learning and troubleshooting. Let's combine AI with traditional methods to master R effectively.

This overview isn't exhaustive of all possible AI tools for R coding, but I believe it is a good start and covers everything you need.


**Make sure to enable Github Copilot in RStudio.**
Go to Tools -> Global Options -> Copilot -> Enable Git

## Learning Goals: 
*At the end of this exercise, you will be able to:*  
1. Explain what AI is and what AI tools can be used for R.
2. Enable Github Copilot in RStudio.
3. Use Copilot/ChatGPT to write code in RStudio.
4. Use Copilot/ChatGPT for troubleshooting code in RStudio.


## Exploration Questions:
Lets get some get a feel for what copilot (or ChatGPT) does, use Github Copilot to autocomplete the questions below. You can alternatively paste the questions in ChatGPT or Microsoft Copilot.
1. What is AI?

2. What is ChatGPT?
chatgpt is the openai language model that can be used to generate human like text. It is a powerful tool that can be used to generate code, write essays, and even answer questions.
3. What is Github Copilot?
Github Copilot is an AI tool that can be used to generate code in RStudio. It is a powerful tool that can be used to generate code, write essays, and even answer questions.
4. [Try it yourself: Insert your own question here]
What is the episode of the office where Michael Scott burns his foot on a George Foreman grill?
Answer: Season 2, Episode 12 "The Injury"

## Load the libraries  
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(dplyr)
library(shiny)
library(shinydashboard)
```



```{r}
library(shiny)

ui <- fluidPage(
  titlePanel("Market Validation Survey"),
  
  selectInput("transport_type", "1. What type of transport do you use to get around?",
              choices = c("Walking", "Bike", "Skateboard", "Car", "Public Transit")),
  
  conditionalPanel(
    condition = "input.transport_type === 'Car' || input.transport_type === 'Walking' || input.transport_type === 'Public Transit'",
    radioButtons("used_micro_mobility", "1.1.1 Have you ever utilized micro-mobility vehicles, such as a bike as one of your primary forms of transport?",
                 choices = list("Yes" = "Yes", "No" = "No"))
  ),
  
  conditionalPanel(
    condition = "input.used_micro_mobility === 'No'",
    textInput("reason_avoid_micro_mobility", "1.1.1.2. Why have you avoided forms of micro-mobility?")
  ),
  
  conditionalPanel(
    condition = "input.transport_type === 'Bike'",
    textInput("primary_reason_bike", "3. What's the primary reason that you chose a bike as your transportation tool"),
    textAreaInput("incident_bike", "4. Tell us about a recent incident, worry, unsafe or uncomfortable that you have had with using a bike for transportation."),
    textAreaInput("distress_causes", "5. What about that causes you distress?"),
    radioButtons("avoid_situations", "6. Do you do anything to avoid situations such as these?",
                 choices = list("Yes" = "Yes", "No" = "No"))
  ),
  
  conditionalPanel(
    condition = "input.avoid_situations === 'Yes'",
    textInput("solution_not_great", "6.1.1. What about your current solution is not great?")
  ),
  
  conditionalPanel(
    condition = "input.avoid_situations === 'No'",
    textInput("desired_improvements", "6.2.1.1. What improvements or features would you like to see in a transportation option to address these safety concerns or discomforts?")
  ),
  
  actionButton("submit", "Submit")
)

server <- function(input, output, session) {
  observeEvent(input$submit, {
    # Data processing would go here
    # In practice, you would &#8203;``【oaicite:0】``&#8203;
    
    responses <- data.frame(
  TransportType = input$transport_type,
  UsedMicroMobility = input$used_micro_mobility,
  ReasonAvoidMicroMobility = input$reason_avoid_micro_mobility,
  PrimaryReasonBike = input$primary_reason_bike,
  IncidentBike = input$incident_bike,
  DistressCauses = input$distress_causes,
  AvoidSituations = input$avoid_situations,
  SolutionNotGreat = input$solution_not_great,
  DesiredImprovements = input$desired_improvements,
  stringsAsFactors = FALSE
)

# This is where you'd typically write to a file or a real database
print(responses)

# You could also send a confirmation message to the user or reset the form
shinyalert::shinyalert("Thank you for completing the survey!", type = "success")
  })
}

```

## Load the Data: 
```{r}
#load the Netflix Data in your Data folder, save it under the object name netflix
netflix <- read_csv("data/netflix_titles.csv")


```

*Did copilot help you write the code above? Could anything about the prompt be improved to help Copilot understand what you want to do more accurately?*



## Lets Practice:
Explore the elements in your data: include a comment within your code chunk to prompt Copilot to use the function of your choice
```{r}
#use the function of your choice to get an idea of the overall structure of the data frame, including its dimensions, column names, variable classes, etc. As part of this, determine if there are NA's and how they are treated.
glimpse(netflix)



```
#*Did copilot use your preferred method to get the summary of the data? If not, how could you improve the prompt to get the desired output?*
No. I like the summary function better. 
```{r}


#Sort out the movies from the netflix into an new object called netflix_movies
```

```{r} 
netflix_movies <- netflix %>% 
  filter(type == "Movie")


```


Which director has the most movies on netflix?
```{r}
#write code
netflix_movies %>% 
  count(director, sort = TRUE)




```
*Do you see anything wrong with the table above, look at row 1. Write a prompt below to fix this.*


romove the nas from the table
```{r}
#write code
netflix_movies %>% 
  count(director, sort = TRUE) %>% 
  filter(!is.na(director))
```

```{r}

```



Which director had the most movies by release year and remove the NA's?
```{r}


```
*See anything else interesting about this table, look at the first director on the table. Could this be a problem and how can we edit the dataset to fix this? Try writing a prompt.*


Put the collarborate directors in a new column, and remove the nas from the table
```{r}
#write code:
netflix_movies %>% 
  separate_rows(director, sep = ",") %>% 
  count(director, sort = TRUE) %>% 
  filter(!is.na(director))
```

Make a bar plot of the top directors with the most movies on netflix
```{r}
#code
netflix_movies %>% 
  separate_rows(director, sep = ",") %>% 
  count(director, sort = TRUE) %>% 
  filter(!is.na(director)) %>% 
  top_n(10) %>% 
  ggplot(aes(x = fct_reorder(director, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Top 10 Directors with the Most Movies on Netflix",
       x = "Director",
       y = "Number of Movies") +
  theme_minimal()





```
#change the bar color to the color of luke's lightsaber:
```{r}
#code
netflix_movies %>% 
  separate_rows(director, sep = ",") %>% 
  count(director, sort = TRUE) %>% 
  filter(!is.na(director)) %>% 
  top_n(10) %>% 
  ggplot(aes(x = fct_reorder(director, n), y = n)) +
  geom_col(color = "green", fill = "green", alpha = 0.75) +
  coord_flip() +
  labs(title = "Top 10 Directors with the Most Movies on Netflix",
       x = "Director",
       y = "Number of Movies") +
  theme_minimal()
```

#change the bar color to the colors of ranbow but in low satuation:
```{r}
#code:
netflix_movies %>% 
  separate_rows(director, sep = ",") %>% 
  count(director, sort = TRUE) %>% 
  filter(!is.na(director)) %>% 
  top_n(10) %>% 
  ggplot(aes(x = fct_reorder(director, n), y = n)) +
  geom_col(color = "rainbow", fill = "rainbow", alpha = 0.25) +
  coord_flip() +
  labs(title = "Top 10 Directors with the Most Movies on Netflix",
       x = "Director",
       y = "Number of Movies") +
  theme_minimal()

```

```{r}
#code
netflix_movies %>% 
  separate_rows(director, sep = ",") %>% 
  count(director, sort = TRUE) %>% 
  filter(!is.na(director)) %>% 
  top_n(10) %>% 
  ggplot(aes(x = fct_reorder(director, n), y = n)) +
  geom_col(color = "rainbow", fill = "rainbow", alpha = 0.25) +
  coord_flip() +
  labs(title = "Top 10 Directors with the Most Movies on Netflix",
       x = "Director",
       y = "Number of Movies") +
  theme_minimal()
```


*Do you see any issues with this plot? How could we improve the prompt to get a better boxplot? Try writing a prompt.*

[Insert your prompt here]
```{r}

```

*How about for just 2020*



[Insert your prompt here]
```{r}

```


*Take a few minutes to make your own plot(s) using prompts, edit prompts until you get a plot that you like.*






## Lets make the top 10 directors barplot into a Shiny App: use copilot or Chatgpt

```{r}
#code:
ui <- dashboardPage(
  dashboardHeader(title = "Top 10 Directors with the Most Movies on Netflix"),
  dashboardSidebar(),
  dashboardBody(
    fluidRow(
      box(title = "Plot Options", width = 3,
          selectInput("x", "Select Director", choices = c("Davis", "Irvine", "Berkeley", "Irvine", "Los_Angeles", "Merced", "Riverside", "San_Diego", "Santa_Barbara", "Santa_Cruz"),
                      selected = "Davis"),
          selectInput("z", "Select Admit Category", choices = c("Applicants", "Admits", "Enrollees"),
                      selected = "Applicants"),
          radioButtons("y", "Select)
    
```
fix the code:
```{r}
#code:
ui <- dashboardPage(
  dashboardHeader(title = "Top 10 Directors with the Most Movies on Netflix"),
  dashboardSidebar(),
  dashboardBody(
    fluidRow(
      box(title = "Plot Options", width = 3,
          selectInput("x", "Select Director", choices = c("Davis", "Irvine", "Berkeley", "Irvine", "Los_Angeles", "Merced", "Riverside", "San_Diego", "Santa_Barbara", "Santa_Cruz"),
                      selected = "Davis"),
          selectInput("z", "Select Admit Category", choices = c("Applicants", "Admits", "Enrollees"),
                      selected = "Applicants"),
          radioButtons
```






kable(netflix_movies %>% 
  separate_rows(director, sep = ",") %>% 
  count(director, sort = TRUE) %>% 
  filter(!is.na(director)) %>% 
  top_n(10))

```{r}


## That's it! Let's take a break and then move on to working on group projects.
